NEFSC multispecies model keyrun project

### 2021-03-22 docs/GBFleetDefinitions.Rmd

All gear types which catch any amount of the [Species](https://noaa-edab.github.io/ms-keyrun/SpeciesEnvDat.html#focalSpecies) of interest are used in the cluster analysis.
```{r echo=T,eval=F}
focalSpecies <- readRDS(here::here("data","focalspecies.rds"))
clusterObj <- cluster_by_focal_species(focalSpecies)
plot(clusterObj,ask=T,which.plots=2,main="All gear types that land species of interest",xlab="")
```

@@

>>>>

All gear types which catch any amount of the [Species](https://noaa-edab.github.io/ms-keyrun/SpeciesEnvDat.html#focalSpecies) of interest are used in the cluster analysis. The hope was the set of gear types in which to begin the cluster analysis would be substantially less. The number of gears eliminated = 10. It is apparent that species of interest are caught across a broad class of gear types.

```{r echo=T,eval=F}
focalSpecies <- readRDS(here::here("data","focalspecies.rds"))
clusterObj <- cluster_by_focal_species(focalSpecies)
plot(clusterObj,ask=T,which.plots=2,main="All gear types that land species of interest",xlab="")
```

@@

## Decision

This exploratory study resulted in the following designation of [Fleets](https://noaa-edab.github.io/ms-keyrun/GBFleetDecision.html)

### 2021-03-22 docs/index.Rmd
add survey/catch dat csvs for hydra
add NOBA hydra sizebins

@@

>>>>

<a href="https://noaa-edab.github.io/ms-keyrun/GBFleetDefinitions.html" target="_blank"> Fleet Definitions - 26 Feb 2021 </a>

* <a href="https://noaa-edab.github.io/ms-keyrun/GBFleetDecisions.html" target="_blank"> Fleet Decisions </a>

@@

<a href="https://noaa-edab.github.io/ms-keyrun/SimData.html" target="_blank"> Initial simulated data for testing - 17 March 2021 </a>
